Supplement 1: Testing different distributions

### 2018-09-15 pkg/disttree/inst/draft/supplement/supplement_distributions.Rnw
revised versions of supplement 1 and 2
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2283 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 13a7f6f3c52fe3004fd87673ab56c156c7cb84e3

Alltogether it can be stated that the left-censored at zero Gaussian distribution seems to be an appropriate choice while the other two distributions are possible and mostly also reasonable alternatives. However, they do not lead to an overall improvement in performance for this application.

@@

\section{Discussion}
As mentioned by \cite{Hofner+Mayr+Schmid:2016} the methods provided by GAMLSS ``can be unstable, especially when it comes to selecting possibly different sets of variables for multiple distribution parameters''. These problems have also occured in a few situations for the 
prespecified GAMLSS model within the cross-validation. In case of this method failing to 
build a model it is represented by \code{NA}s in the evaluation.

>>>>

@@

\section{Discussion}
Alltogether it can be stated that the left-censored at zero Gaussian distribution seems to be an appropriate choice while the other two distributions are possible and mostly also reasonable alternatives. However, they do not lead to an overall improvement in performance for this application.
